Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

\extraspacing {\bf Computing the ``d-cross'' Sets.} We are ready to compute $\dcross_H(\bm{t})$, defined in \eqref{eqn:dcross-H}, for any $\bm{t} \in \J(R'_1, ..., R'_{k-2})$, thanks to Statement (2) of Lemma~\ref{lmm:hv:type1:cross-r*}. First, compute $B_\bm{t}$, obtain the rectangle $r' = \gbot(\bm{t})$, and fetch the (already computed) top-sliced rectangle $r^*$ of $r'$; these steps require $O(k)$ time. Then, scan the segments in $\cross_H(r^*)$ in ascending order of their y-coordinates. For each segment $h$ scanned, check whether $h$ belongs to $\dcross_H(\bm{t})$, namely, whether $h$ crosses both $B_\bm{t}$ and $\gbot(\bm{t})$; this can be done in constant time. Abort the scan as soon as $h \notin \dcross_H(\bm{t})$. This way, we produce $\dcross_H(\bm{t})$ in $O(k + |\dcross_H(\bm{t}|))$ time. Doing so for all $\bm{t} \in \J(R'_1, ..., R'_{k-2})$ takes $O(k \cdot |\J| + \sum_\bm{t} |\dcross_H(t)|) = O(k \cdot \out)$ time, where the derivation used statement (2) of Lemma~\ref{lmm:hv:type1:properties}.

>>>>

\extraspacing {\bf Computing the ``d-cross'' Sets.} We are ready to compute $\dcross_H(\bm{t})$, defined in \eqref{eqn:dcross-H}, for any $\bm{t} \in \J(R'_1, ..., R'_{k-2})$, thanks to Statement (2) of Lemma~\ref{lmm:hv:type1:cross-r*}. First, compute $B_\bm{t}$, obtain the rectangle $r' = \gbot(\bm{t})$, and fetch the (already computed) top-sliced rectangle $r^*$ of $r'$; these steps require $O(k)$ time. Then, scan the segments in $\cross_H(r^*)$ in ascending order of their y-coordinates. For each segment $h$ scanned, check whether $h$ belongs to $\dcross_H(\bm{t})$, namely, whether $h$ crosses $B_\bm{t}$ (the reader can verify that $h$ must cross $\gbot(\bm{t})$); this can be done in constant time. Abort the scan as soon as $h \notin \dcross_H(\bm{t})$. This way, we produce $\dcross_H(\bm{t})$ in $O(k + |\dcross_H(\bm{t}|))$ time. Doing so for all $\bm{t} \in \J(R'_1, ..., R'_{k-2})$ takes $O(k \cdot |\J| + \sum_\bm{t} |\dcross_H(t)|) = O(k \cdot \out)$ time, where the derivation used statement (2) of Lemma~\ref{lmm:hv:type1:properties}.
